Capstone Movielens Report

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Fix for helper functions review: Model regularization process.

::: {.noteblock data-latex=""}
In the code snippet above this function is used as a parameter to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.

>>>>

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Regularization Functions] of *This Appendix*.
